Portal Forecast

### 2018-02-15 index.Rmd
Cleanup report.Rmd

obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "period"))
obs_data_newmoon$censusdate = as.Date(obs_data_newmoon$censusdate)
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")

>>>>

obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "period"))
obs_data_newmoon$censusdate = as.Date(obs_data_newmoon$censusdate)
